Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-03 sections/eval.tex
Update on Overleaf.

We used finch to implement two fundamental graph algorithms: Breadth-First Search (BFS) and Bellman-Ford single-source shortest path. Our BFS implementation and graphs datasets are taken from Yang et. al \cite{yang_implementing_2018}, including road networks, characterized by bounded node degrees and long diameters, and scale-free graphs, where node degree distribution follows a power-law distribution and diameters are short.

>>>>

We used finch to implement two fundamental graph algorithms: Breadth-First Search (BFS) and Bellman-Ford single-source shortest path. Our BFS implementation and graphs datasets are taken from Yang et al.~\cite{yang_implementing_2018}, including road networks, characterized by bounded node degrees and long diameters, and scale-free graphs, where node degree distribution follows a power-law distribution and diameters are short.
